Plant-pollintor networks worldwide are composed by the same specific building

### 2021-08-03 Draft/Draft.Rmd
Update Draft.Rmd

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4."}

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="Figure 4. Graphical representation of the probability of finding a given functional group $x$ in the position $\\alpha$ of motif $i$, $p_i(x,\\alpha)$, for all the possible motifs from two to five species in bipartite networks. The slices in the nodes for a given functional group $x$ are proportional to the corresponding value of $p_i(x,\\alpha)$."}
